A Technique for Inter-Catalogue Recommendations

### 2014-06-10 paper2/paper.tex
Rework the introduction.

\section*{Introduction}
Recommender systems have become a critical component for online retailers in
nearly every space of retail. Whether the products are movies or clothes or
research articles, large retailers tend to have a way of recommending products
based on others previously viewed or purchased products.

These recomendations usually come from a combination of content-based
information and collaborative filtering techniques. The content-based approach
uses information about the products, such as category or description, to connect
related products. Alone, however, this approach is usually unable to capture the
subtle ways products may actually be related. Collaborative filtering, on the
other hand, learns relations from aggregated user behavior.  Such
recommendations often have explicit titles like ``People who liked this product
also liked these products''. Collaborative filtering has proven to be effective
at recommending products, given that there is a large amount of user data.

Since each retailer only has user data within their site, these user-based
recommender systems are good at learning connections between products in one
catalogue, but they do little to learn how these products may relate to other
products outside of the retailer's inventory. This type of information is
valuable in a number of situations. Retailers such as department stores want to
know which new products make the most sense to add to their catalogue.  This is
essentially a question of recommending the best outside products based on
current in-house ones. In a different scenario, two retailers may merge and want
to construct a unified recommender system between the two catalgoues.

We model this as a problem of connecting recommender systems between disjoint
catalogues. The goal is to construct good recommendations from products in one
catalogue to products in the other. These catalogues may be from competing
retailers who don't have access to each other's user data. Thus, to keep the
problem general, we do not assume that we have any private data.
Instead, we constrain ourselves to use only the product information and internal
recommendations that are posted publicly to all users.

This is a difficult problem. What makes a good recommendation is hard to define
objectively. One can say that if users co-purchase or co-view products together,
then these products should be recommended for each other. But without any user
data, it is hard to simulate this kind of user behavior. The connections between
co-viewed products are often less tangible than simple metrics of similarity.

In this paper, we outline a technique that leverages the intra-catalogue
recommendations of each catalogue to construct inter-catalgoue recommendations
between them. We focus on clothing retailers, since they tend to all have
public recommendations for each product. Specifically, the data used for this
project was all collected from the public product webpages for Macy's.

\section*{Data}
For this work, we utilize most of the product catalog of Macy's as presented at
www.macys.com. This catalog consists of numerous categories of mostly apparel,
each of which includes hundreds to thousands of items. We confine this study to
the 49 categories within the two main parent categories ``Men'' and ``Women''
that contain at least 200 items that are associated to multiple brands. In
total, this dataset consists of 66,071 items in 49 categories with some items
listed in multiple categories. For each item we record its description, all
categories within which it is listed, and its associated recommendations. By
{\em recommendations}, we are referring to the items---there are typically four
in the case of Macy's---that are displayed on a product's details page under the
heading ``Customers Also Shopped''. The presence of these recommendations
implicitly forms a directed graph over the product catalogue, in which the nodes
are the {\em products} or {\em items} and the edges are the {\em
recommendations}. We call these types of graphs {\em recommendation graphs} and
they play a central role in this study.

@@

\bibitem{Powers2011}
    Powers, David M W.
    ``Evaluation: From Precision, Recall and F-Measure to ROC, Informedness,
Markedness \& Correlation.''
    \emph{Journal of Machine Learning Technologies} \textbf{2}, 37-63, 2011.

>>>>

\section*{Introduction}
A key challenge in retail is choosing which items to incorporate into one's
collection of offered goods and services. These decisions can significantly
impact a retailer's revenue in the short run as well as affect customer
experience, and hence, their relationship with the retailer. Several factors
must be considered including the number of product lines, the variety of
products in each line, as well as the consistency and relationships between
products. In this study, we focus on the latter and explore techniques that
leverage publicly available product recommendation information for the purpose
of improving product assortment decisions.

It has become standard practice for online retailers to recommend one or more
products to prospective customers who have viewed or purchased an item. These
recommendations are generally derived from either content-based approaches or
via collaborative filtering, utilizing data-mining techniques \cite{Ricci2011}.
Importantly, these recommendations provide a source of publicly available
business intelligence by relating the items in their respective catalogue.
Specifically, these online recommendations logically form a directed graph in
which the nodes are products and an edge pointing from item $A$ to item $B$
indicates that customers who view or purchase item $A$ are recommended item $B$.
Given the recommendation graphs of two or more distinct retailers, our goal is
to determine new, meaningful edges that connect these graphs in a way that would
allow one retailer to relate their products to those of another.

Content-based approaches and collaborative filtering have distinct challenges,
and therefore, offer unique advantages as solutions to the general recommender
problem.  An effective content-based solution requires a detailed analysis of
item and/or user profile information. A well-known, successful example is the
Music Genome Project, which powers the music service Pandora \cite{mgp}. Such an
approach can be difficult, however, since necessary user and/or item information
might be unavailable or the required domain expertise might be too costly. The
alternative method is that of collaborative filtering (CF), which leverages the
correlations within user purchase or rating data. The idea is that two items
that tend to be purchased or highly rated by the same users can be considered
related such that if a new user likes one they will probably like the other. A
key advantage of this approach is that it effectively outsources the
recommendation problem to the retailer's customers. Online retailers such as
Amazon.com and Netflix are known to employ recommender systems based on CF
\cite{Koren2009}. At the same time, CF notoriously suffers from what is known as
the {\em cold start}---without user-item data of sufficient quantity and
diversity these systems fail to yield accurate results.

The problem we examine here is, in many ways, more difficult than that of the
standard recommendation problem. Essentially, we would like to recommend an item
from retailer $X$ based solely on a known preference for an item from retailer
$Y$. For the product assortment problem, user purchase and rating information is
presumably known for one of the two retailers. In this study, however, we
simplify the scenario by making it symmetric. No user purchase or rating
information will be leveraged for either retailer. Instead, the algorithms
investigated here are limited to publicly available information, which includes
product descriptions and online product recommendations. Given the lack of
inter-retailer user data, a CF technique is ostensibly not an option. The
obvious approach is therefore content-based.

In this report. . . . (BREIFLY OUTLINE THE PAPER HERE.)

\section*{Data}
For this work, we utilize most of the product catalogue of Macy's as presented
at www.macys.com. This catalogue consists of numerous categories of mostly
apparel, each of which includes hundreds to thousands of items. We confine this
study to the 49 categories within the two main parent categories ``Men'' and
``Women'' that contain at least 200 items that are associated to multiple
brands. In total, this dataset consists of 66,071 items in 49 categories with
some items listed in multiple categories. For each item we record its
description, all categories within which it is listed, and its associated
recommendations. By {\em recommendations}, we are referring to the items---there
are typically four in the case of Macy's---that are displayed on a product's
details page under the heading ``Customers Also Shopped''. The presence of these
recommendations implicitly forms a directed graph over the product catalogue, in
which the nodes are the {\em products} or {\em items} and the edges are the {\em
recommendations}. We call these types of graphs {\em recommendation graphs} and
they play a central role in this study.

@@

\bibitem{Ricci2011}
    Francesco Ricci, Lior Rokach, and Bracha Shapira.
    \emph{Introduction to Recommender Systems Handbook}, Springer, 1-35, 2011.

\bibitem{mgp}
    For information on the Music Genome Project, visit
    http://www.pandora.com/about/mgp

\bibitem{Koren2009}
    Yehuda Koren, Robert Bell, and Chris Volinsky.
    ``Matrix factorization techniques for recommender systems.''
    \emph{Computer} 42.8, 2009. 30-37.

\bibitem{Powers2011}
    David M W Powers.
    ``Evaluation: From Precision, Recall and F-Measure to ROC, Informedness,
Markedness \& Correlation.''
    \emph{Journal of Machine Learning Technologies} \textbf{2}, 37-63, 2011.
